### 2017-02-02 doc/manual/version3/inputParameters.tex
added xDotDerivativeScheme to manual

>>>>

\param{xDotDerivativeScheme}
{integer}
{0}
{Whenever \parlink{includeXDotTerm} is \true.}
{Changes the differentiation matrix used for the collisionless $\dot{x} \propto E_r$ term. This parameter
does not affect the differentiation matrix used for the energy scattering part of the collision operator.\\

{\ttfamily xDotDerivativeScheme} = 0: Use the same differentiation matrix for the $\dot{x}$ term as for the collision operator.\\

{\ttfamily xDotDerivativeScheme} = 11: Use a low-order tri-diagonal differentiation matrix for the $\dot{x}$ term.\\

Other values of {\ttfamily xDotDerivativeScheme} have been implemented (see {\ttfamily createGrids.F90}) but are
not recommended. The recommended setting is almost always {\ttfamily xDotDerivativeScheme} = 0.
The one exception is sometimes when \parlink{magneticDriftScheme}$>0$, in which
case the convergence with respect to \parlink{Nx} is sometimes poor for values of $E_r$ near the peak in the radial fluxes.
In this case, {\ttfamily xDotDerivativeScheme} = 11 may resolve the problem.
}
